### 2013-02-24 article.tex
Format inline code
Signed-off-by: Michael Barton <mail@michaelbarton.me.uk>

Genomer uses these two libraries to create a plugin system where third-party
software can be written and included. Plugin creators need only to prefix the
name of their plugin with `genomer-plugin-' and upload this to rubygems.org or
make the plugin available as a public git repository. A plugin is specified
within the project in a file named `Gemfile.' The `bundle update` command will
then automatically download and install the required plugins.

Genomer is implemented as a command line tool and tested on both Mac OS X and
Linux systems. The latest version of genomer can installed from the Rubygems
package management system with the command `gem install genomer`. Genomer is
then invoked on the command line with the command `genomer`. Genomer provides
extensive documentation via man pages and on the genomer website at
http://next.gs.

@@

This software was written for the command-line to use in shells such as bash or
zsh. Command line tools are simple to automate using scripting, allowing
reproducible genome finishing and sharing genome projects between researchers.
For instance, during our microbial genome project we automated Genomer using
GNU Make build files, allowing the finishing steps to be repeated automatically
using the `make` command. Additionally we stored each version of the GNU Make
build file with git \cite{git-scm} to track changes to the project and to allow
errors to be reverted from earlier versions. Example build files from our
genome projects can be found on GitHub for a simple plasmid
\cite{plasmid-github} and more complex \cite{genome-github} sequence.

We divided this tool into modular parts each called a `plugin.' Genomer
provides no functionality itself, but rather serves to make the functionality
of plugins available for use at the command line. For example to validate the
correctness of genome annotations, the genomer-plugin-validate plugin should be
installed which then allows the required functionality to be through the
`genomer` command. Presently, we have developed and released three plugins:
viewing a genome sequence in common bioinformatics file formats, validating the
correctness of genome annotations for common errors, and provide summaries of a
genome sequence. Each of these plugins are available on GitHub and their use
described is in the documentation at http://next.gs.

@@

\item{The genomer-plugin-view plugin is then added to the Gemfile in the root
of the project directory. The command `bundle update`, run in the project root,
will then download and install this plugin making it available for use in the
Genomer project.}

\item{Different views can then be generated from the scaffold using the
`genomer view` command. For instance, a GFF3 file of the scaffolded annotations
may be generated. Should the originating contig annotations or the genome
scaffold be changed then rerunning the `genomer view` command will
correspondingly update the annotation coordinates for the scaffold.}

>>>>

Genomer uses these two libraries to create a plugin system where third-party
software can be written and included. Plugin creators need only to prefix the
name of their plugin with \verb+genomer-plugin-+ and upload this to
rubygems.org or make the plugin available as a public git repository. A plugin
is specified within the project in a file named `Gemfile.' The \verb+bundle update+
command will then automatically download and install the required plugins.

Genomer is implemented as a command line tool and tested on both Mac OS X and
Linux systems. The latest version of genomer can installed from the Rubygems
package management system with the command \verb+gem install genomer+. Genomer
is then invoked on the command line with the command \verb+genomer+. Genomer
provides extensive documentation via man pages and on the genomer website at
http://next.gs.

@@

This software was written for the command-line to use in shells such as bash or
zsh. Command line tools are simple to automate using scripting, allowing
reproducible genome finishing and sharing genome projects between researchers.
For instance, during our microbial genome project we automated Genomer using
GNU Make build files, allowing the finishing steps to be repeated automatically
using the \verb+make+ command. Additionally we stored each version of the GNU
Make build file with git \cite{git-scm} to track changes to the project and to
allow errors to be reverted from earlier versions. Example build files from our
genome projects can be found on GitHub for a simple plasmid
\cite{plasmid-github} and more complex \cite{genome-github} sequence.

We divided this tool into modular parts each called a `plugin.' Genomer
provides no functionality itself, but rather serves to make the functionality
of plugins available for use at the command line. For example to validate the
correctness of genome annotations, the genomer-plugin-validate plugin should be
installed which then allows the required functionality to be through the
\verb+genomer+ command. Presently, we have developed and released three
plugins: viewing a genome sequence in common bioinformatics file formats,
validating the correctness of genome annotations for common errors, and provide
summaries of a genome sequence. Each of these plugins are available on GitHub
and their use described is in the documentation at http://next.gs.

@@

\item{The genomer-plugin-view plugin is then added to the Gemfile in the root
of the project directory. The command \verb+bundle update+, run in the project
root, will then download and install this plugin making it available for use in
the Genomer project.}

\item{Different views can then be generated from the scaffold using the
\verb+genomer view+ command. For instance, a GFF3 file of the scaffolded
annotations may be generated. Should the originating contig annotations or the
genome scaffold be changed then rerunning the \verb+genomer view+ command will
correspondingly update the annotation coordinates for the scaffold.}
